---
title: "Mode in R - Central Tendency Analysis for NYC Housing"
output: html_notebook
---

```{r message=FALSE, warning=FALSE, error=TRUE}
# Load required libraries
library(readr)
library(dplyr)
library(DescTools)
```

## Data Loading & Preparation

In this section, we import one-bedroom apartment rental data for Brooklyn, Manhattan, and Queens from StreetEasy datasets and extract the rental prices into numeric vectors.

```{r message=FALSE, warning=FALSE, error=TRUE}
# Read in housing data
brooklyn_one_bed <- read_csv('brooklyn-one-bed.csv')
brooklyn_price <- brooklyn_one_bed$rent

manhattan_one_bed <- read_csv('manhattan-one-bed.csv')
manhattan_price <- manhattan_one_bed$rent

queens_one_bed <- read_csv('queens-one-bed.csv')
queens_price <- queens_one_bed$rent
```

---

## Task 1: Calculate Mean Rent

*Instructions: Calculate the arithmetic mean rental price for each borough and assign the values to `brooklyn_mean`, `manhattan_mean`, and `queens_mean`.*

```{r error=TRUE}
# Calculate Mean
# Hint: Use mean(vector_name, na.rm = TRUE)

brooklyn_mean <- NULL
manhattan_mean <- NULL
queens_mean <- NULL
```

---

## Task 2: Calculate Median Rent

*Instructions: Calculate the median rental price for each borough and assign the values to `brooklyn_median`, `manhattan_median`, and `queens_median`.*

```{r error=TRUE}
# Calculate Median
# Hint: Use median(vector_name, na.rm = TRUE)

brooklyn_median <- NULL
manhattan_median <- NULL
queens_median <- NULL
```

---

## Task 3: Calculate Mode Rent

*Instructions: Calculate the statistical mode for each borough using `DescTools::Mode()`. Extract the primary modal value and assign to `brooklyn_mode`, `manhattan_mode`, and `queens_mode`.*

```{r error=TRUE}
# Calculate Mode
# Note: Base R mode() returns data storage type, NOT statistical mode!
# Hint: Mode(vector_name)[1]

brooklyn_mode <- NULL
manhattan_mode <- NULL
queens_mode <- NULL
```

---

## Task 4: Summary Table Construction

*Instructions: Build a clean summary table (tibble) compiling all three measures across all three boroughs.*

```{r error=TRUE}
# Construct a summary data frame using dplyr/tibble
summary_table <- tibble(
  Borough = c("Brooklyn", "Manhattan", "Queens"),
  Mean_Rent = c(brooklyn_mean, manhattan_mean, queens_mean),
  Median_Rent = c(brooklyn_median, manhattan_median, queens_median),
  Mode_Rent = c(brooklyn_mode, manhattan_mode, queens_mode)
)

print(summary_table)
```

---

## Validation & Verification Output

```{r error=TRUE}
# Mean Verification
if(!is.null(brooklyn_mean) && exists('brooklyn_mean')) {
  print(paste("The mean price in Brooklyn is $" , round(brooklyn_mean, digits=2))) 
} else {
  print("The mean price in Brooklyn is not yet defined.")
}

if(!is.null(manhattan_mean) && exists("manhattan_mean")) {
  print(paste("The mean price in Manhattan is $" , round(manhattan_mean, digits=2)))
} else {
  print("The mean in Manhattan is not yet defined.")
}

if(!is.null(queens_mean) && exists("queens_mean")) {
  print(paste("The mean price in Queens is $" , round(queens_mean, digits=2)))
} else {
  print("The mean price in Queens is not yet defined.")
}   
    
# Median Verification
if(!is.null(brooklyn_median) && exists("brooklyn_median")) {
  print(paste("The median price in Brooklyn is $" , brooklyn_median)) 
} else {
  print("The median price in Brooklyn is not yet defined.")
}

if(!is.null(manhattan_median) && exists("manhattan_median")) {
  print(paste("The median price in Manhattan is $" , manhattan_median))
} else {
  print("The median in Manhattan is not yet defined.")
}

if(!is.null(queens_median) && exists("queens_median")) {
  print(paste("The median price in Queens is $" , queens_median))
} else {
  print("The median price in Queens is not yet defined.")
} 
    
# Mode Verification
if(!is.null(brooklyn_mode) && exists("brooklyn_mode")) {
  print(paste("The mode price in Brooklyn is $" , brooklyn_mode)) 
} else {
  print("The mode price in Brooklyn is not yet defined.")
}

if(!is.null(manhattan_mode) && exists("manhattan_mode")) {
  print(paste("The mode price in Manhattan is $" , manhattan_mode))
} else {
  print("The mode in Manhattan is not yet defined.")
}

if(!is.null(queens_mode) && exists("queens_mode")) {
  print(paste("The mode price in Queens is $" , queens_mode))
} else {
  print("The mode price in Queens is not yet defined.")
}
```