---
title: "Explore the 1985 Cars Dataset"
output: html_notebook
---

## Introduction

You collect cars, and your collection is missing a car from 1985. We have a
dataset of 1985 cars (from the UCI Machine Learning Repository) that we can
analyze to help decide which car to add to the collection.

Work through each task below. Each task has a corresponding code chunk —
fill it in with the requested R code.

---

## Loading and Inspecting the Data

### Task 1: Load the tidyverse packages you'll need (`readr`, `dplyr`)

```{r}
# YOUR CODE HERE

```

### Task 2: Load `cars85.csv` into a dataframe called `cars`

```{r}
# YOUR CODE HERE

```

### Task 3: Inspect `cars` with `head()` and `summary()`

```{r}
# YOUR CODE HERE

```

> What kind of information do you have? What can you do with this information?

---

## Clean the Data

### Task 4: Remove the `normalized_losses` column

Select all columns from `cars` except `normalized_losses`. Save the result
back to `cars`.

```{r}
# YOUR CODE HERE

```

### Task 5: Print the column names of `cars`

Are they clear and descriptive?

```{r}
# YOUR CODE HERE

```

### Task 6: Rename `symboling` to `risk_factor`

Update the column name, then print the column names again to confirm.

```{r}
# YOUR CODE HERE

```

---

## Add a Column

### Task 7: Create a variable `mpg_threshold` with the value 30

```{r}
# YOUR CODE HERE

```

### Task 8: Add a column `mpg_diff_from_threshold`

This should measure how far each car's highway mpg is from `mpg_threshold`.
View the updated `cars` dataframe.

```{r}
# YOUR CODE HERE

```

---

## Filter and Arrange Rows

### Task 9: Filter to cars where `mpg_diff_from_threshold` > 0

Save the result to `mpg_exceeds_threshold` and view it.

```{r}
# YOUR CODE HERE

```

### Task 10: Arrange `mpg_exceeds_threshold` by `mpg_diff_from_threshold` descending

Save the result back to `mpg_exceeds_threshold`.

```{r}
# YOUR CODE HERE

```

### Task 11: Order `cars` by `engine_size` descending

Save the result to `ordered_by_engine_size` and view it.

```{r}
# YOUR CODE HERE

```

---

## Specifying the Make of the Car

### Task 12: Create a variable `chosen_make`

Set it to a make you're interested in, e.g. one of: `alfa-romero`, `audi`,
`bmw`, `chevrolet`, `dodge`, `honda`, `isuzu`, `jaguar`, `mazda`,
`mercedes-benz`, `mercury`, `mitsubishi`, `nissan`, `peugot`, `plymouth`,
`porsche`, `renault`, `saab`, `subaru`, `toyota`, `volkswagen`, `volvo`.

```{r}
# YOUR CODE HERE

```

### Task 13: Filter `cars` to rows where `make == chosen_make`

Save the result to `chosen_make_details`.

```{r}
# YOUR CODE HERE

```

### Task 14: Order `chosen_make_details` by `engine_size` descending

Save the result back to `chosen_make_details` and view it.

```{r}
# YOUR CODE HERE

```

> How large are the engines in each of the cars from that make? Try
> changing `chosen_make` and re-running to explore other makes.

---

## Task 15: Wrap-up

Reflect: based on your analysis, which 1985 car would you add to your
collection, and why?

*(no code required — just make your decision!)*
