---
title: "Explore the 1985 Cars Dataset — Solution"
output: html_notebook
---

## Introduction

You collect cars, and your collection is missing a car from 1985. We have a
dataset of 1985 cars (from the UCI Machine Learning Repository) that we can
analyze to help decide which car to add to the collection.

---

## Loading and Inspecting the Data

### Task 1: Load the tidyverse packages

```{r}
library(readr)
library(dplyr)
```

### Task 2: Load `cars85.csv` into `cars`

```{r}
cars <- read_csv("cars85.csv")
```

### Task 3: Inspect `cars`

```{r}
head(cars)
summary(cars)
```

Each row is a single car; each column is a characteristic of that car
(make, body style, engine specs, mileage, price, etc). This gives us
everything we need to compare cars against each other before "buying".

---

## Clean the Data

### Task 4: Remove the `normalized_losses` column

`normalized_losses` is full of `?` placeholders (missing values), so we
drop it rather than try to work around the missing data.

```{r}
cars <- cars %>% select(-normalized_losses)
```

### Task 5: Print the column names

```{r}
colnames(cars)
```

Most names are clear, but `symboling` isn't self-explanatory.

### Task 6: Rename `symboling` to `risk_factor`

```{r}
cars <- cars %>% rename(risk_factor = symboling)
colnames(cars)
```

---

## Add a Column

### Task 7: Create `mpg_threshold`

```{r}
mpg_threshold <- 30
```

### Task 8: Add `mpg_diff_from_threshold`

```{r}
cars <- cars %>% mutate(mpg_diff_from_threshold = highway_mpg - mpg_threshold)
cars
```

---

## Filter and Arrange Rows

### Task 9: Filter to cars exceeding the threshold

```{r}
mpg_exceeds_threshold <- cars %>% filter(mpg_diff_from_threshold > 0)
mpg_exceeds_threshold
```

### Task 10: Arrange by `mpg_diff_from_threshold` descending

```{r}
mpg_exceeds_threshold <- mpg_exceeds_threshold %>%
  arrange(desc(mpg_diff_from_threshold))
mpg_exceeds_threshold
```

### Task 11: Order `cars` by `engine_size` descending

```{r}
ordered_by_engine_size <- cars %>% arrange(desc(engine_size))
ordered_by_engine_size
```

---

## Specifying the Make of the Car

### Task 12: Create `chosen_make`

```{r}
chosen_make <- "volvo"
```

### Task 13: Filter `cars` to the chosen make

```{r}
chosen_make_details <- cars %>% filter(make == chosen_make)
chosen_make_details
```

### Task 14: Order `chosen_make_details` by `engine_size` descending

```{r}
chosen_make_details <- chosen_make_details %>% arrange(desc(engine_size))
chosen_make_details
```

Swap the value of `chosen_make` (e.g. `"toyota"`, `"bmw"`, `"porsche"`) and
re-run Tasks 12–14 to compare engine sizes across other makes.

---

## Task 15: Wrap-up

Using the tables above — cars sorted by highway mpg efficiency, cars
sorted by engine size, and the engine sizes within your favorite make —
you now have everything you need to pick the best 1985 car for your
collection. Congratulations on the new addition!
